Title

### 2015-12-10 paper/paper.tex
add feature weights for order scorer

@@

The mean, standard deviation, min and max for both the baseline and greedy
approach are reported in the table below.

>>>>

\begin{table}
\centering
\begin{tabular}{|r|c|c|}
\hline
Feature & Weight \\ \hline\hline
mean pairwise Jaccard & -5.00181089 \\ \hline
std\_dev pairwise Jaccard & -0.33312514 \\ \hline
min pairwise Jaccard & 2.60603159 \\ \hline
max pairwise Jaccard & 1.55569119 \\ \hline
mean two-apart Jaccard & 4.19364855 \\ \hline
std\_dev two-apart Jaccard & 7.77286275 \\ \hline
min two-apart Jaccard & 2.94073393 \\ \hline
max two-apart Jaccard & -4.35272278 \\ \hline
mean pairwise node Jaccard & -0.94370112 \\ \hline
std\_dev pairwise node Jaccard & 4.49617236 \\ \hline
min pairwise node Jaccard & 1.14357291 \\ \hline
max pairwise node Jaccard & -1.94888156 \\ \hline
mean combined Jaccard & 0.47908235 \\ \hline
std\_dev combined Jaccard & -1.84644112 \\ \hline
min combined Jaccard & -0.57636185 \\ \hline
max combined Jaccard & 0.82229913 \\ \hline
\end{tabular}
\caption{Feature weights for Subrgaph Order Scorer}
\end{table}

@@

The mean, standard deviation, min and max for both the baseline and greedy
Kendall tau  are reported in the table below.
